%% Vloženie rôznych nastavení
\input{header-before}

\def \nazovUlohy{Lab 2 - Simple, flawed Server}
\def \skola{\textbf{Chalmers university - Computer science}}
\def \tema{Homework from computer networks}
\def \author{\textbf{Michal Šustr}, \textbf{Arnaud D'Artigues}}
\def \email{\href{mailto:michal.sustr@gmail.com}{\texttt{michal.sustr@gmail.com}} \\ \href{mailto:arnaud.dartigues@gmail.com}{\texttt{arnaud.dartigues@gmail.com}}}
\def \date{8. 9. 2014}

%% Pokračovanie nastavení
\input{header-after}

\begin{document}

%% Úvodná stránka
\input{firstpage}

\section{Answers to lab questions}
\subsection*{Question I.a.1}
The symbolic name of the address in the code is \texttt{INADDR\_ANY} and it is \texttt{0.0.0.0}.

\subsection*{Question I.a.2}
From the manual of \texttt{recv}:
\begin{quote}
Return  the  number  of bytes received, or -1 if an error occurred.  The return value will be 0 when the peer  has  performed  an orderly shutdown.
\end{quote}
This answers the cases a), b) and c). The last case d) \texttt{ret=kTransferBufferSize} means that the buffer is completely filled. 

\texttt{cd.buffer} is defined to be of size \texttt{kTransferBufferSize+1} because in C we need to include the \texttt{NULL} terminating character.

\subsection*{Question I.a.3}
The connection is closed/reset if the return value is -1 and error code of value \texttt{ECONNRESET}.

\texttt{MSG\_NOSIGNAL} flag stops generating \texttt{SIGPIPE} signals on stream oriented sockets when the other end breaks the connection, the \texttt{EPIPE} signal is still generated indicating if the  local  end  has  been  shut  down  on a connection oriented socket.
 
\subsection*{Question I.c.1}
When we connect with the first client, it can send and receive messages. Once a second connection with another client is established, it can send a message but gets blocked until the first client disconnects. When we do a netstat, we can see that for both clients, the connection with the server is \texttt{ESTABLISHED}, which means their sockets are truly connected.

\subsection*{Question I.c.2}
Once the first client gets disconnected, it receives response from the server. The server is iterative, so it can handle requests only from one client at a time until it disconnects. Then the next client can be served.

\subsection*{Question I.c.3}
The round trip time on the same machine depends on the length of the message, it varies from $0.1ms$ to $0.0001ms$. If the message length is the same as \texttt{kTransferBufferSize}, the 5 measured times are:
$0.000212 ms$, $0.000189 ms$, $0.000205 ms$, $0.000172 ms$, $0.000222 ms$ with average $\overline{T_{same}} = 0.0002 ms$.

We connected to different machine, and the measured round trip times are $185.15 ms$, $236.51 ms$, $231.71 ms$, $544.55 ms$ and $269.42 ms$, with average $\overline{T_{different}} = 293.46 ms$.

\subsection*{Question I.d.1}
We ran the command \texttt{./client-multi localhost 31336 7 255} with following measurements:
\begin{verbatim}
Establishing 7 connections... 
  successfully initiated 7 connection attempts!
Connect timing results for 7 successful connections
  - min time: 0.366060 ms
  - max time: 0.549235 ms
  - average time: 0.461344 ms
 (0 connections failed!)
Roundtrip timing results for 7 connections for 255 round trips
  - min time: 10159.585865 ms
  - max time: 71119.216374 ms
  - average time: 40639.376403 ms
\end{verbatim}

Some other records:
\begin{verbatim}
Establishing 10 connections... 
  successfully initiated 10 connection attempts!
Connect timing results for 10 successful connections
  - min time: 0.103116 ms
  - max time: 0.218299 ms
  - average time: 0.138663 ms
 (0 connections failed!)
Roundtrip timing results for 10 connections for 255 round trips
  - min time: 10160.063502 ms
  - max time: 101603.979012 ms
  - average time: 55882.432563 ms
\end{verbatim}

\begin{verbatim}
Establishing 15 connections... 
  successfully initiated 15 connection attempts!
Connect timing results for 15 successful connections
  - min time: 0.382923 ms
  - max time: 3001.949394 ms
  - average time: 333.608482 ms
 (0 connections failed!)
Roundtrip timing results for 15 connections for 255 round trips
  - min time: 10158.026511 ms
  - max time: 151399.968558 ms
  - average time: 80944.698838 ms
\end{verbatim}

\subsection*{Question I.d.3}
We measured the time from beginning of the connection until error in $recv$ was obtained as a difference of timestamps from \texttt{get\_time\_stamp()}. On average, the time is $\overline{T_{timeout}}=34371.25 ms$.


%\begin{thebibligraphy}{5}
%\textsc{	\bibitem{ari}
%		\emph{Polynomiální metody - Michael Šebek} \\
%		\url{http://www.polyx.com/_ari/slajdy/Pr-ARI-19-Polynom.pdf}
%}
%\end{thebibliography}

\end{document}